Type-Safe Modular Parsing

### 2017-05-18 SLE_17/sections/Introduction.tex
Shorten conclusion. Resize table.

Syntactic modularization techniques have also been applied to the
problem of \emph{extensible parsing}. There are several approaches
that enable the development of \emph{syntactically} modular parsers or
grammars. Many parser
generators~\cite{antlr1995,Grimm2006,Gouseti2014,Warth2016} support
modular grammars. For instance, \textit{Rats!}~\cite{Grimm2006} has
its own module system for the collection of grammars.  Extensible
compilers like JastAdd~\cite{Ekman2007} and
Polyglot~\cite{Nystrom2003} also support extensible parsing, but this
is mostly done ultimately resorting to standard (non-modular) parser
generators. Various techniques supporting languages that can extend
their own syntax, such as SugarJ~\cite{Erdweg2011}, also offer a form
of extensible parsing. However since those approaches are syntactic
they do not support separate compilation and/or modular type-checking
of parsing code either.

>>>>

Syntactic modularization techniques have also been applied to the
problem of \emph{extensible parsing}. Many parser
generators~\cite{antlr1995,Grimm2006,Gouseti2014,Warth2016} support
modular grammars. For instance, \textit{Rats!}~\cite{Grimm2006} has
its own module system for the collection of grammars.  Extensible
compilers like JastAdd~\cite{Ekman2007} and
Polyglot~\cite{Nystrom2003} also support extensible parsing, but this
is mostly done ultimately resorting to standard (non-modular) parser
generators. Various techniques supporting languages that can extend
their own syntax, such as SugarJ~\cite{Erdweg2011}, also offer a form
of extensible parsing. However those syntactic approaches do not
support separate compilation and/or modular type-checking
of parsing code either.

### 2017-05-18 SLE_17/sections/RelatedWork.tex
Shorten conclusion. Resize table.

It is worth mentioning that Scala case classes~\cite{emir2007matching} provide a near
solution to the Expression Problem. Case classes can be
modularly added, but they do not enforce
exhaustiveness of pattern matching for extensible operations. In other
words run-time pattern matching errors can happen when writing extensible code with case classes. So that full static type-safety is not ensured. Nevertheless case classes are a pragmatic approach, which is
widely used in practice. Therefore, modular parsing techniques may be
of value for extensible code using case classes.  The approach we
presented in Section~\ref{sec:inheritance} can readily be adapted to case classes:
all that the users need to do is to use case classes, instead of
standard OO classes in their code.\haoyuan{To simplify; conclusion}

>>>>

It is worth mentioning that Scala case classes~\cite{emir2007matching} provide a near
solution to the Expression Problem. Case classes can be
modularly added, but they do not enforce
exhaustiveness of pattern matching for extensible operations. In other
words run-time pattern matching errors can happen when writing extensible code with case classes. So that full static type-safety is not ensured. Nevertheless case classes are a pragmatic approach, which is
widely used in practice. Therefore, modular parsing techniques may be
of value for extensible code using case classes.  The approach we
presented in Section~\ref{sec:inheritance} can readily be adapted to case classes:
all that the users need to do is to use case classes, instead of
standard OO classes in their code.
